An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-15 ex3/paper/paper.tex
Add ars results finally

\todo{Insert results}

>>>>

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and average modification per flow required by an adversary to make a flow appear benign for CIC-IDS-2017.}
\label{fig:recall_ars}
\end{figure}

\autoref{fig:recall_ars} shows that certain attack types, like ``DoS Slowloris'' are easy to classify for an IDS but still are also surprisingly easy for an attacker to perform adversarial modifications to make them look benign.
